FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-16 paper.tex
rearrange outline

\begin{abstract}
  Reliable numerical computations are central to high-performance computing and machine learning.
  We present FlowFPX: a Julia-based tool for tracking the onset and flow of IEEE Floating-Point exceptions that signal numerical defects.
  FlowFPX's design exploits Julia's operator overloading to trace exception flows and even inject exceptions to accelerate testing.
  We present intuitive visualizations of summarized exception flows including how they are generated, propagated and killed, thus helping with debugging and repair.
\end{abstract}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FlowFPX}{FlowFPX}
\newcommand{\FloatTracker}{FloatTracker}
\newcommand{\FT}{\FloatTracker}
\newcommand{\CSTG}{stack graph}
\newcommand{\CPP}{\code{C++}}
\newcommand{\Dendro}{\textsc{Dendro}}
\newcommand{\urlaccess}[2]{\url{#1}}

@@

\subsection{FloatTracker}
% I'd love to find some Sherlock Holmes title for this section, as it would be a subtle nod to Sherlogs.jl and would be a nice literary reference to compliment "To Kill a Mockingbird"

@@

\section{FloatTracker Internals}

@@

\FT{} is an effective tool for debugging all sorts of NaN-related issues.
We have used it to reveal silent NaNs, uncover the root cause of NaNs,
and fuzz for weak points in several case studies.

@@

\section{Evaluation}

>>>>

\begin{abstract}
  Reliable numerical computations are central to high-performance computing and machine learning.
  We present FlowFPX: a Julia-based tool for tracking the onset and flow of IEEE floating point exceptions.
  FlowFPX's design exploits Julia's operator overloading to trace exception flows and even inject exceptions to accelerate testing.
  We present intuitive visualizations of summarized exception flows including how they are generated, propagated and killed, thus helping with debugging and repair.
\end{abstract}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FlowFPX}{FlowFPX}
\newcommand{\GPUFPX}{GPU-FPX}
\newcommand{\FloatTracker}{FloatTracker}
\newcommand{\FT}{\FloatTracker}
\newcommand{\CSTG}{stack graph}
\newcommand{\CPP}{\code{C++}}
\newcommand{\Dendro}{\textsc{Dendro}}
\newcommand{\urlaccess}[2]{\url{#1}}

@@

kk

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig/genpropkill-outline.png}
  \caption{Gen, Prop, Kill: Lifetime of a NaN value}
  \label{f:gpk}
\end{figure}

\section{FlowFPX Toolkit}

@@

\FlowFPX{} is effective for debugging all sorts of NaN-related issues.
We have used it to reveal silent NaNs, uncover the root cause of NaNs,
and fuzz for weak points in several case studies.

@@

\subsection{\GPUFPX{}: Oceananigans}

FILL

% * what about GPUs? companion project at Utah GPU-FPX
% * architecture diagram, CPU + GPU, show Ocean source code
% * replace CPU() with GPU() in code, get output like below & attached
% 
% \begin{verbatim}
% using Oceananigans
% grid = RectilinearGrid(GPU(), size=(128, 128), x=(0, 2π), y=(0, 2π), topology=(Periodic, Periodic, Flat))
% model = NonhydrostaticModel(; grid, advection=WENO())
% ϵ(x, y, z) = 2rand() - 1
% set!(model, u=ϵ, v=ϵ)
% simulation = Simulation(model; Δt=0.01, stop_time=4)
% run!(simulation)
% \end{verbatim}
% 
% ... xinyi ran gpu-fpx on this code ... on the binary it created?
% 
% 
% - - -
% 
% 
% #GPU-FPX LOC-EXCEP INFO: in kernel
% [_Z27julia_broadcast_kernel_716715CuKernelContext13CuDeviceArrayI7ComplexI7Float64ELi3ELi1EE11BroadcastedI12CuArrayStyleILi3EE5TupleI5OneToI5Int64ES6_IS7_ES6_IS7_EE2__S5_IS3_IS4_ILi3EEvS8_S5_I8ExtrudedIS0_IS1_IS2_ELi3ELi1EES5_I4BoolS10_S10_ES5_IS7_S7_S7_EEEES3_IS4_ILi3EEvS8_S5_IS3_IS4_ILi3EEvS8_S5_IS9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EEEES7_EEEES7_],
% DIV0 found @ ./float.jl:335 [FP64]
% #GPU-FPX LOC-EXCEP INFO: in kernel
% [_Z27julia_broadcast_kernel_716715CuKernelContext13CuDeviceArrayI7ComplexI7Float64ELi3ELi1EE11BroadcastedI12CuArrayStyleILi3EE5TupleI5OneToI5Int64ES6_IS7_ES6_IS7_EE2__S5_IS3_IS4_ILi3EEvS8_S5_I8ExtrudedIS0_IS1_IS2_ELi3ELi1EES5_I4BoolS10_S10_ES5_IS7_S7_S7_EEEES3_IS4_ILi3EEvS8_S5_IS3_IS4_ILi3EEvS8_S5_IS9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EEEES7_EEEES7_],
% NaN found @ ./float.jl:335 [FP64]
% #GPU-FPX LOC-EXCEP INFO: in kernel
% [_Z27julia_broadcast_kernel_716715CuKernelContext13CuDeviceArrayI7ComplexI7Float64ELi3ELi1EE11BroadcastedI12CuArrayStyleILi3EE5TupleI5OneToI5Int64ES6_IS7_ES6_IS7_EE2__S5_IS3_IS4_ILi3EEvS8_S5_I8ExtrudedIS0_IS1_IS2_ELi3ELi1EES5_I4BoolS10_S10_ES5_IS7_S7_S7_EEEES3_IS4_ILi3EEvS8_S5_IS3_IS4_ILi3EEvS8_S5_IS9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EEEES7_EEEES7_],
% NaN found @ ./float.jl:335 [FP32]
% #GPU-FPX LOC-EXCEP INFO: in kernel
% [_Z27julia_broadcast_kernel_716715CuKernelContext13CuDeviceArrayI7ComplexI7Float64ELi3ELi1EE11BroadcastedI12CuArrayStyleILi3EE5TupleI5OneToI5Int64ES6_IS7_ES6_IS7_EE2__S5_IS3_IS4_ILi3EEvS8_S5_I8ExtrudedIS0_IS1_IS2_ELi3ELi1EES5_I4BoolS10_S10_ES5_IS7_S7_S7_EEEES3_IS4_ILi3EEvS8_S5_IS3_IS4_ILi3EEvS8_S5_IS9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EEEES7_EEEES7_],
% DIV0 found @ ./int.jl:261 [FP64]
% #GPU-FPX LOC-EXCEP INFO: in kernel
% [_Z27julia_broadcast_kernel_716715CuKernelContext13CuDeviceArrayI7ComplexI7Float64ELi3ELi1EE11BroadcastedI12CuArrayStyleILi3EE5TupleI5OneToI5Int64ES6_IS7_ES6_IS7_EE2__S5_IS3_IS4_ILi3EEvS8_S5_I8ExtrudedIS0_IS1_IS2_ELi3ELi1EES5_I4BoolS10_S10_ES5_IS7_S7_S7_EEEES3_IS4_ILi3EEvS8_S5_IS3_IS4_ILi3EEvS8_S5_IS9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EEEES7_EEEES7_],
% NaN found @ ./int.jl:261 [FP64]
% #GPU-FPX LOC-EXCEP INFO: in kernel
% [_Z27julia_broadcast_kernel_716715CuKernelContext13CuDeviceArrayI7ComplexI7Float64ELi3ELi1EE11BroadcastedI12CuArrayStyleILi3EE5TupleI5OneToI5Int64ES6_IS7_ES6_IS7_EE2__S5_IS3_IS4_ILi3EEvS8_S5_I8ExtrudedIS0_IS1_IS2_ELi3ELi1EES5_I4BoolS10_S10_ES5_IS7_S7_S7_EEEES3_IS4_ILi3EEvS8_S5_IS3_IS4_ILi3EEvS8_S5_IS9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EES9_IS0_IS2_Li3ELi1EES5_IS10_S10_S10_ES5_IS7_S7_S7_EEEES7_EEEES7_],
% INF found @ ./int.jl:261 [FP64]
% 
% 
% \begin{verbatim}
% --- GPU-FPX Report ---
% 
% --- FP64 Operations ---
% Total NaN found: 2
% Total INF found: 1
% Total underflow (subnormal): 0
% Total division by zero: 2
% --- FP32 Operations ---
% Total NaN found: 1
% Total INF found: 0
% Total underflow (subnormal): 0
% Total division by zero: 0
% --- Other Stats ---
% Kernels: 21
% \end{verbatim}
